Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-08-26 tex/covidEffectOfNPI-revision.tex

We now turn our focus to dynamic feedback effects. Policy
and behavior changes that reduce case and death growth today can lead to a more
optimistic, riskier behavior in the future, attenuating longer run effects.
We perform the main counterfactual experiments using the average of two estimated coefficients as reported in column ``Average'' of Table \ref{tab:dieff-si} under a specification that excludes the number of past national cases and deaths from information variables. In the appendix, we also report additional counterfactual experiment results with the specification that includes the national information variables, and find that they are very similar. The results on mask policies, business closures, stay-at-home orders are robust with respect to this variation (see Figures \ref{fig:US-mask}-\ref{fig:US-shelter} in the appendix). On the other hand, the results on removing all policies, particularly closure of schools, reported in the next section, are sensitive to the inclusion of national information variables, highlighting the large uncertainty regarding the size of the effect.  In Figures \ref{fig:WA-mask}-\ref{fig:US-shelter} below, the top panel presents the result on cases while the bottom panel presents the result on deaths.

%Additional counterfactual experiments include the
%} %\footnote{\textbf{The results of counterfactual experiments are not sensitive to whether we use the estimate of  table \ref{tab:dieff-si} or that of table \ref{tab:dieff} except for a counterfactual experiment of removing all policies  in section \ref{removing-policies}.}}

@@

\begin{figure}[ht]
  \caption{Effect of mandating masks on April 1st in Washington State \label{fig:WA-mask}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{ccc}
      \multicolumn{3}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-growth}
      &
        \includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-dgrowth_v1}
      &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-dcases_v1}
      \\
      \\
      \multicolumn{3}{c}{\textbf{Deaths}}
      \\      \includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-growth_deaths}
      &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-dgrowth_deaths_v1}
      &      \includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-dcases_deaths_v1}
    \end{tabular}
    \begin{flushleft}
      \footnotesize To compute the estimated and counterfactual paths
      we use the average of two estimated coefficients as reported in
      column ``Average'' of Table \ref{tab:dieff-si}. We set initial
      $\Delta \log \Delta C$ and $\log \Delta C$ to their values first
      observed in the state we are simulating. We hold all other
      regressors at their observed values. Error terms are drawn with
      replacement from the residuals. We do this many times and report
      the average over draws of the residuals. The shaded region is a
      point-wise 90\% confidence interval.
    \end{flushleft}
  \end{minipage}
\end{figure}

@@

For illustrative purpose, we begin by focusing on Washington State.
The
left column of  Figure \ref{fig:WA-mask} shows the observed, estimated
average, and counterfactual average of $\Delta \log \Delta C$ (top panel) and
$\Delta \log \Delta D$ (bottom panel). To compute the estimated and counterfactual
paths, we use the   estimate   in
column ``Average'' of Table \ref{tab:dieff-si}. We set initial
$\Delta \log \Delta C$ and $\log \Delta C$ to their values first
observed in the state we are simulating. We hold all other regressors
at their observed values. Error terms are drawn with replacement from
the residuals. We do this many times and report the average over draws
of the residuals. The shaded region is a point-wise 90\% confidence
interval. The left column shows that the fit of the estimated and
observed growth rate is quite good.

The middle column of Figure \ref{fig:WA-mask} shows the change in
growth rate from mandating masks on April 1st. The shaded region is a
90\% pointwise confidence interval. As shown, mandating masks on April
1st lowers the growth of cases or deaths 14 or 21 days later by 0.1 to
0.15. This effect then gradually declines due to information
feedback. Mandatory masks reduce past cases or deaths, which leads to
less cautious behavior, attenuating the impact of the policy. The
reversal of the decrease in growth in late April is due to our
comparison of a mask mandate on April 1st with Washington's actual
mask mandate in early May. By late April, the counterfactual mask
effect has decayed through information feedback, and we are comparing
it the undecayed impact of Washington's actual, later mask mandate.

The right column of Figure \ref{fig:WA-mask} shows how the changes in
case and death growth translate into changes in cases and deaths. The
estimates imply that mandating masks on April 1st would have led to
500 fewer cases and 250 fewer deaths in Washington in total by the start of
June.

\begin{figure}[ht]
  \caption{Effect of nationally mandating masks for employees on April
    1st in the US\label{fig:US-mask}}
  \begin{minipage}{\linewidth}
    \centering
    \medskip
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-dgrowth_v1}
      &
        \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-rel_v1}
      \\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
      \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-dgrowth_deaths_v1}
      &
        \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-rel_deaths_v1}
    \end{tabular}
  \end{minipage}
    \begin{flushleft}
      \footnotesize In the left column, the dots are the average
      change in growth in each state. The blue line is the average
      across states of the change in growth. The shaded region is a
      point-wise 90\% confidence interval. The right column shows the
      change in cases or deaths relative to the baseline of actual
      policies.
    \end{flushleft}
\end{figure}

The results for other states are similar to those for Washington. In
the appendix, Figures  \ref{fig:MA-mask} and \ref{fig:IL-mask} display
similar results for Massachusetts and Illinois.
Figure \ref{fig:US-mask} shows the average change in cases and
deaths across states, where the top panel shows the effect on cases and the bottom panel shows the effect on deaths.
The point estimates indicate that mandating masks on April 1st
could have led to 25\% fewer cumulative cases and 37\% fewer
cumulative deaths by the end of May with their 90 percent intervals given by $[10,47]$\% and $[18,55]$\%, respectively. The result roughly translates into $18$ to $55$ thousand saved lives.

\subsection{Non-essential Business Closures}

A particularly controversial policy is the closure of non-essential
businesses. We now examine a counterfactual where non-essential
businesses are never closed. Figure \ref{fig:WA-nb} shows the effect
of leaving non-essential businesses open in Washington. The point
estimate implies that the closure of non-essential businesses reduced cases and
deaths by a small amount. However, this estimate is relatively
imprecise; 90\% confidence intervals for the change in cases and deaths from
leaving non-essential businesses open by the end of May are [-250,700] and
[-100,1200], respectively.

\begin{figure}[ht]
  \caption{Effect of leaving non-essential businesses open in Washington \label{fig:WA-nb}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/Washington-nb-dgrowth_v1}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/Washington-nb-dcases_v1}\\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/Washington-nb-dgrowth_deaths_v1}
      & \includegraphics[width=0.45\textwidth]{tables_and_figures/Washington-nb-dcases_deaths_v1}
    \end{tabular}
  \end{minipage}
\end{figure}

Figure \ref{fig:US-nb} shows the national effect of leaving non
essential businesses open on cases and deaths. For cases, the
estimates imply that with non-essential businesses open, cases would
be about -15 to 60\% higher in late May. The results for deaths are
similar but less precise.

\begin{figure}[ht]
  \caption{Effect of leaving non-essential businesses open in the US\label{fig:US-nb}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-nb-dgrowth_v1}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-nb-rel_v1}
      \\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-nb-dgrowth_deaths_v1}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-nb-rel_deaths_v1}
    \end{tabular}
  \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
  \caption{Effect of having no stay-at-home orders in the US\label{fig:US-shelter}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-dgrowth_v1}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-rel_v1}
      \\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-dgrowth_deaths_v1}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-rel_deaths_v1}
    \end{tabular}
  \end{minipage}
\end{figure}

@@

@@

\subsection{Counterfactuals for Massachusetts and
  Illinois}
 Figures \ref{fig:MA-mask} and \ref{fig:IL-mask} present the fit of estimated cases as well as the counterfactual effect of mandating masks on April 1st in Massachusetts and Illinois, respectively. Figures \ref{fig:MA-nb} and \ref{fig:IL-nb}   show the counterfactual effect of leaving non-essential business open in Massachusetts and Illinois, respectively.

\begin{figure}[b]
  \caption{Effect of mandating masks on April 1st in Massachusetts \label{fig:MA-mask}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{ccc}
      \multicolumn{3}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-growth}
      &
        \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dgrowth_v1}
      &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dcases_v1}
\\
      \multicolumn{3}{c}{\textbf{Deaths}} \\
     \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-growth_deaths}
      &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dgrowth_deaths_v1}
      &      \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dcases_deaths_v1}
    \end{tabular}
    \begin{flushleft}
      \footnotesize To compute the estimated and counterfactual paths
      we use the average of two estimated coefficients as reported in
      column ``Average'' of Table \ref{tab:dieff}. We set initial
      $\Delta \log \Delta C$ and $\log \Delta C$ to their values first
      observed in the state we are simulating. We hold all other
      regressors at their observed values. Error terms are drawn with
      replacement from the residuals. We do this many times and report
      the average over draws of the residuals. The shaded region is a
      point-wise 90\% confidence interval.
    \end{flushleft}
  \end{minipage}
\end{figure}

\begin{figure}[h]
  \caption{Effect of mandating masks on April 1st in Illinois \label{fig:IL-mask}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{ccc}
      \multicolumn{3}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-growth}
      &
        \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dgrowth_v1}
      &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dcases_v1}      \\
      \multicolumn{3}{c}{\textbf{Deaths}} \\
    \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-growth_deaths}
      &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dgrowth_deaths_v1}
      &      \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dcases_deaths_v1}
    \end{tabular}
    \begin{flushleft}
      \footnotesize To compute the estimated and counterfactual paths
      we use the average of two estimated coefficients as reported in
      column ``Average'' of Table \ref{tab:dieff}. We set initial
      $\Delta \log \Delta C$ and $\log \Delta C$ to their values first
      observed in the state we are simulating. We hold all other
      regressors at their observed values. Error terms are drawn with
      replacement from the residuals. We do this many times and report
      the average over draws of the residuals. The shaded region is a
      point-wise 90\% confidence interval.
    \end{flushleft}
  \end{minipage}
\end{figure}

\begin{figure}[h]
  \caption{Effect of leaving businesses open in Massachusetts \label{fig:MA-nb}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dgrowth_v1}
       &
         \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dcases_v1}
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
        \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dgrowth_deaths_v1}
       &      \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dcases_deaths_v1}
    \end{tabular}
  \end{minipage}
\end{figure}

\begin{figure}[h]
  \caption{Effect of leaving businesses open in Illinois \label{fig:IL-nb}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dgrowth_v1}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dcases_v1} \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
           \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dgrowth_deaths_v1}
      &       \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dcases_deaths_v1}    \end{tabular}
  \end{minipage}
\end{figure}

@@

>>>>

We now turn our focus to dynamic feedback effects. Policy and behavior
changes that reduce case and death growth today can lead to a more
optimistic, riskier behavior in the future, attenuating longer run
effects.  We perform the main counterfactual experiments using the
average of two estimated coefficients as reported in column
``Average'' of Table \ref{tab:dieff-con-si} under a specification that
excludes the number of past national cases and deaths from information
variables and constrains masks to have only direct effects and
business policies only indirect effects.\footnote{Results (not shown)
  using the unconstrained estimates in Table \ref{tab:dieff-si} are similar.}
%In the appendix, we also report additional counterfactual
%experiment results with the specification that includes the national
%information variables, and find that they are very similar.
% The results on mask policies, business closures, stay-at-home orders
% are robust with respect to this variation (see Figures
% \ref{fig:US-mask}-\ref{fig:US-shelter} in the appendix). On the other
% hand, the results on removing all policies, particularly closure of
% schools, reported in the next section, are sensitive to the inclusion
% of national information variables, highlighting the large uncertainty
% regarding the size of the effect.  In Figures
% \ref{fig:WA-mask}-\ref{fig:US-shelter} below, the top panel presents
% the result on cases while the bottom panel presents the result on
% deaths.

@@

\begin{figure}[ht]
  \caption{Effect of mandating masks on April 1st in Washington State \label{fig:WA-mask}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      %\includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-growth}
      % &
        \includegraphics[width=0.49\textwidth]{tables_and_figures/Washington-mask-dgrowth_idx}
      &        \includegraphics[width=0.49\textwidth]{tables_and_figures/Washington-mask-dcases_idx}
      \\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}}
      \\
      % \includegraphics[width=0.31\textwidth]{tables_and_figures/Washington-mask-growth_deaths} &
                                                                                                   \includegraphics[width=0.49\textwidth]{tables_and_figures/Washington-mask-dgrowth_deaths_idx}
      &      \includegraphics[width=0.49\textwidth]{tables_and_figures/Washington-mask-dcases_deaths_idx}
    \end{tabular}

    \begin{flushleft}
      \footnotesize
      The vertical (often truncated) text denotes the
      dates that Washington imposed each policy.  To compute the
      estimated and counterfactual paths we use the average of two
      estimated coefficients as reported in column ``Average'' of
      Table \ref{tab:dieff-con-si}. We set initial
      $\Delta \log \Delta C$ and $\log \Delta C$ to their values first
      observed in the state we are simulating. We hold all other
      regressors at their observed values. The shaded region is a
      point-wise 90\% confidence interval.
    \end{flushleft}
  \end{minipage}
\end{figure}

@@

For illustrative purpose, we begin by focusing on Washington State.
% The
% left column of  Figure \ref{fig:WA-mask} shows the observed, estimated
% average, and counterfactual average of $\Delta \log \Delta C$ (top panel) and
% $\Delta \log \Delta D$ (bottom panel). To compute the estimated and counterfactual
% paths, we use the   estimate   in
% column ``Average'' of Table \ref{tab:dieff-si}. We set initial
% $\Delta \log \Delta C$ and $\log \Delta C$ to their values first
% observed in the state we are simulating. We hold all other regressors
% at their observed values. Error terms are drawn with replacement from
% the residuals. We do this many times and report the average over draws
% of the residuals. The shaded region is a point-wise 90\% confidence
% interval. The left column shows that the fit of the estimated and
% observed growth rate is quite good.
The left column of Figure \ref{fig:WA-mask} shows the change in
growth rate from mandating masks on April 1st. The shaded region is a
90\% pointwise confidence interval. As shown, mandating masks on April
1st lowers the growth of cases or deaths 14 or 21 days later by 0.1 to
0.15. This effect then gradually declines due to information
feedback. Mandatory masks reduce past cases or deaths, which leads to
less cautious behavior, attenuating the impact of the policy. The
reversal of the decrease in growth in late April is due to our
comparison of a mask mandate on April 1st with Washington's actual
mask mandate in early May. By late April, the counterfactual mask
effect has decayed through information feedback, and we are comparing
it the undecayed impact of Washington's actual, later mask mandate.

The right column of Figure \ref{fig:WA-mask} shows how the changes in
case and death growth translate into changes in cases and deaths. The
estimates imply that mandating masks on April 1st would have led to
about 300 fewer cases and 10 fewer deaths in Washington in total by
the start of June.

\begin{figure}[ht]
  \caption{Effect of nationally mandating masks for employees on April
    1st in the US\label{fig:US-mask}}
  \begin{minipage}{\linewidth}
    \centering
    \medskip
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-dgrowth_idx}
      &
        \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-rel_idx}
      \\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
      \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-dgrowth_deaths_idx}
      &
        \includegraphics[width=0.49\textwidth]{tables_and_figures/us-mask-rel_deaths_idx}
    \end{tabular}

    \begin{flushleft}
      \footnotesize In the left column, the dots are the average
      change in growth in each state. The blue line is the average
      across states of the change in growth. The shaded region is a
      point-wise 90\% confidence interval for the national average
      change in growth. The right column shows the change in cases or
      deaths relative to the baseline of actual policies.
    \end{flushleft}
  \end{minipage}
\end{figure}

The results for other states are similar to those for Washington.
%In
%the appendix, Figures  \ref{fig:MA-mask} and \ref{fig:IL-mask} display
%similar results for Massachusetts and Illinois.
Figure \ref{fig:US-mask} shows the average change in cases and
deaths across states, where the top panel shows the effect on cases and the bottom panel shows the effect on deaths.
The point estimates indicate that mandating masks on April 1st
could have led to 30\% fewer cumulative cases and 34\% fewer
cumulative deaths by the end of May with their 90 percent intervals given by $[13,46]$\% and $[12,47]$\%, respectively. The result roughly translates into $30$ thousand saved lives.

\subsection{Business Closure Policies}

Business closures are particularly controversial. We now examine a
counterfactual where there are no business closure policies (no
restaurant, movie theater, or non-essential business closure).  Figure
\ref{fig:US-business} shows the national effect of never restricting
businesses on cases and deaths. The point estimates imply that,
without business closures, cases and deaths would be about 60\% at the
end of May. The confidence intervals are wide. A 90 percent confidence
interval for the increase in cases at the end of May is 0 to
150\%. The confidence interval for deaths is even wider.

\begin{figure}[ht]
  \caption{Effect of having no business closure policies in the US\label{fig:US-business}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-index-dgrowth_idx}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-index-rel_idx}
      \\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-index-dgrowth_deaths_idx}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-index-rel_deaths_idx}
    \end{tabular}

    \begin{flushleft}
      \footnotesize In the left column, the dots are the average
      change in growth in each state. The blue line is the average
      across states of the change in growth. The shaded region is a
      point-wise 90\% confidence interval for the national average
      change in growth. The right column shows the change in cases or
      deaths relative to the baseline of actual policies.
    \end{flushleft}
  \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
  \caption{Effect of having no stay-at-home orders in the US\label{fig:US-shelter}}
  \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \multicolumn{2}{c}{\textbf{Cases}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-dgrowth_idx}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-rel_idx}
      \\
      \\
      \multicolumn{2}{c}{\textbf{Deaths}} \\
      \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-dgrowth_deaths_idx}
      &
        \includegraphics[width=0.45\textwidth]{tables_and_figures/us-shelter-rel_deaths_idx}
    \end{tabular}

    \begin{flushleft}
      \footnotesize In the left column, the dots are the average
      change in growth in each state. The blue line is the average
      across states of the change in growth. The shaded region is a
      point-wise 90\% confidence interval for the national average
      change in growth. The right column shows the change in cases or
      deaths relative to the baseline of actual policies.
    \end{flushleft}
  \end{minipage}
\end{figure}

@@

[Do we even still need this section?]

@@

% \subsection{Counterfactuals for Massachusetts and
%   Illinois}
%  Figures \ref{fig:MA-mask} and \ref{fig:IL-mask} present the fit of estimated cases as well as the counterfactual effect of mandating masks on April 1st in Massachusetts and Illinois, respectively. Figures \ref{fig:MA-nb} and \ref{fig:IL-nb}   show the counterfactual effect of leaving non-essential business open in Massachusetts and Illinois, respectively.

% \FloatBarrier

% \begin{figure}[b]
%   \caption{Effect of mandating masks on April 1st in Massachusetts \label{fig:MA-mask}}
%   \begin{minipage}{\linewidth}
%     \centering
%     \begin{tabular}{ccc}
%       \multicolumn{3}{c}{\textbf{Cases}} \\
%       \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-growth}
%       &
%         \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dgrowth_v1}
%       &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dcases_v1}
% \\
%       \multicolumn{3}{c}{\textbf{Deaths}} \\
%      \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-growth_deaths}
%       &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dgrowth_deaths_v1}
%       &      \includegraphics[width=0.31\textwidth]{tables_and_figures/Massachusetts-mask-dcases_deaths_v1}
%     \end{tabular}
%     \begin{flushleft}
%       \footnotesize To compute the estimated and counterfactual paths
%       we use the average of two estimated coefficients as reported in
%       column ``Average'' of Table \ref{tab:dieff}. We set initial
%       $\Delta \log \Delta C$ and $\log \Delta C$ to their values first
%       observed in the state we are simulating. We hold all other
%       regressors at their observed values. Error terms are drawn with
%       replacement from the residuals. We do this many times and report
%       the average over draws of the residuals. The shaded region is a
%       point-wise 90\% confidence interval.
%     \end{flushleft}
%   \end{minipage}
% \end{figure}

% \begin{figure}[h]
%   \caption{Effect of mandating masks on April 1st in Illinois \label{fig:IL-mask}}
%   \begin{minipage}{\linewidth}
%     \centering
%     \begin{tabular}{ccc}
%       \multicolumn{3}{c}{\textbf{Cases}} \\
%       \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-growth}
%       &
%         \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dgrowth_v1}
%       &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dcases_v1}      \\
%       \multicolumn{3}{c}{\textbf{Deaths}} \\
%     \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-growth_deaths}
%       &        \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dgrowth_deaths_v1}
%       &      \includegraphics[width=0.31\textwidth]{tables_and_figures/Illinois-mask-dcases_deaths_v1}
%     \end{tabular}
%     \begin{flushleft}
%       \footnotesize To compute the estimated and counterfactual paths
%       we use the average of two estimated coefficients as reported in
%       column ``Average'' of Table \ref{tab:dieff}. We set initial
%       $\Delta \log \Delta C$ and $\log \Delta C$ to their values first
%       observed in the state we are simulating. We hold all other
%       regressors at their observed values. Error terms are drawn with
%       replacement from the residuals. We do this many times and report
%       the average over draws of the residuals. The shaded region is a
%       point-wise 90\% confidence interval.
%     \end{flushleft}
%   \end{minipage}
% \end{figure}

% \begin{figure}[h]
%   \caption{Effect of leaving businesses open in Massachusetts \label{fig:MA-nb}}
%   \begin{minipage}{\linewidth}
%     \centering
%     \begin{tabular}{cc}
%       \multicolumn{2}{c}{\textbf{Cases}} \\
%       \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dgrowth_v1}
%        &
%          \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dcases_v1}
%       \\
%       \multicolumn{2}{c}{\textbf{Deaths}} \\
%         \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dgrowth_deaths_v1}
%        &      \includegraphics[width=0.45\textwidth]{tables_and_figures/Massachusetts-nb-dcases_deaths_v1}
%     \end{tabular}
%   \end{minipage}
% \end{figure}

% \begin{figure}[h]
%   \caption{Effect of leaving businesses open in Illinois \label{fig:IL-nb}}
%   \begin{minipage}{\linewidth}
%     \centering
%     \begin{tabular}{cc}
%       \multicolumn{2}{c}{\textbf{Cases}} \\
%       \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dgrowth_v1}
%       &
%         \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dcases_v1} \\
%       \multicolumn{2}{c}{\textbf{Deaths}} \\
%            \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dgrowth_deaths_v1}
%       &       \includegraphics[width=0.45\textwidth]{tables_and_figures/Illinois-nb-dcases_deaths_v1}    \end{tabular}
%   \end{minipage}
% \end{figure}

@@

\fixme
% DO WE STILL WANT THESE? THESE FIGURES HAVE NOT BEEN UPDATED.
